---
title: "Using machine learning methods to predict physical activity types with Apple Watch and Fitbit data using indirect calorimetry as the criterion."
author: "Arastoo Bozorgi and Daniel Fuller"
date: "07/06/2019"
output:
      html_document:
        keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading the required libraries
```{r warning=FALSE}
library("data.table")
library("dplyr")
library("tidyverse")
library("e1071")
library("caret")
library("rpart")
library("rpart.plot")
library("mlbench")
library("randomForest")
library("stats")
#library("RWeka")
```

## Reading the data

```{r warning=FALSE}
aggregated_data <- read_csv("aggregated_fitbit_applewatch_jaeger.csv")
```

### Descriptive statistics
```{r}
gender_stats <- aggregated_data %>% 
  group_by(id, gender) %>% 
  summarise(
     n()
  ) %>% 
  group_by(gender) %>% 
  summarise(
    freq = n()
    ) %>% 
  mutate(
    percent = (freq / sum(freq)) * 100
    )

identity_stats <- aggregated_data %>% 
  group_by(gender) %>% 
  summarise(
    mean_age = mean(age),
    sd_age = sd(age),
    mean_height = mean(height),
    sd_height = sd(height),
    mean_weight = mean(weight),
    sd_weight = sd(weight),
    mean_Applewatch.Steps_LE = mean(Applewatch.Steps_LE),
    sd_Applewatch.Steps_LE = sd(Applewatch.Steps_LE),
    mean_Applewatch.Heart_LE = mean(Applewatch.Heart_LE),
    sd_Applewatch.Heart_LE = sd(Applewatch.Heart_LE),
    mean_Applewatch.Calories_LE = mean(Applewatch.Calories_LE),
    sd_Applewatch.Calories_LE = sd(Applewatch.Calories_LE),
    mean_Applewatch.Distance_LE = mean(Applewatch.Distance_LE),
    sd_Applewatch.Distance_LE = sd(Applewatch.Distance_LE),
    
    mean_Fitbit.Steps_LE = mean(Fitbit.Steps_LE),
    sd_Fitbit.Steps_LE = sd(Fitbit.Steps_LE),
    mean_Fitbit.Heart_LE = mean(Fitbit.Heart_LE),
    sd_Fitbit.Heart_LE = sd(Fitbit.Heart_LE),
    mean_Fitbit.Calories_LE = mean(Fitbit.Calories_LE),
    sd_Fitbit.Calories_LE = sd(Fitbit.Calories_LE),
    mean_Fitbit.Distance_LE = mean(Fitbit.Distance_LE),
    sd_Fitbit.Distance_LE = sd(Fitbit.Distance_LE)
  ) %>% 
  mutate(
    count = gender_stats$freq,
    percentage = gender_stats$percent,
  )

paper_stats <- aggregated_data %>% 
 # group_by(id) %>% 
  summarise(
    mean_Applewatch.Steps_LE = mean(Applewatch.Steps_LE),
    sd_Applewatch.Steps_LE = sd(Applewatch.Steps_LE),
    mean_Applewatch.Heart_LE = mean(Applewatch.Heart_LE),
    sd_Applewatch.Heart_LE = sd(Applewatch.Heart_LE),
    mean_AppleWatch_EE = mean(Applewatch.Calories_LE, na.rm = T),
    sd_AppleWatch_EE = sd(Applewatch.Calories_LE),
    mean_Applewatch.Distance_LE = mean(Applewatch.Distance_LE),
    sd_Applewatch.Distance_LE = sd(Applewatch.Distance_LE),
    mean_EntropyApplewatchHeartPerDay_LE = mean(EntropyApplewatchHeartPerDay_LE),
    sd_EntropyApplewatchHeartPerDay_LE = sd(EntropyApplewatchHeartPerDay_LE),
    mean_EntropyApplewatchStepsPerDay_LE = mean(EntropyApplewatchStepsPerDay_LE),
    sd_EntropyApplewatchStepsPerDay_LE = sd(EntropyApplewatchStepsPerDay_LE),
    mean_RestingApplewatchHeartrate_LE = mean(RestingApplewatchHeartrate_LE),
    sd_RestingApplewatchHeartrate_LE = sd(RestingApplewatchHeartrate_LE),
    mean_CorrelationApplewatchHeartrateSteps_LE = mean(CorrelationApplewatchHeartrateSteps_LE, na.rm = T),
    sd_CorrelationApplewatchHeartrateSteps_LE = sd(CorrelationApplewatchHeartrateSteps_LE, na.rm = T),
    mean_NormalizedApplewatchHeartrate_LE = mean(NormalizedApplewatchHeartrate_LE),
    sd_NormalizedApplewatchHeartrate_LE = sd(NormalizedApplewatchHeartrate_LE),
    mean_ApplewatchIntensity_LE = mean(ApplewatchIntensity_LE),
    sd_ApplewatchIntensity_LE = sd(ApplewatchIntensity_LE),
    mean_SDNormalizedApplewatchHR_LE = mean(SDNormalizedApplewatchHR_LE),
    sd_SDNormalizedApplewatchHR_LE = sd(SDNormalizedApplewatchHR_LE),
    mean_ApplewatchStepsXDistance_LE = mean(ApplewatchStepsXDistance_LE),
    sd_ApplewatchStepsXDistance_LE = sd(ApplewatchStepsXDistance_LE),
    
    mean_Fitbit.Steps_LE = mean(Fitbit.Steps_LE),
    sd_Fitbit.Steps_LE = sd(Fitbit.Steps_LE),
    mean_Fitbit.Heart_LE = mean(Fitbit.Heart_LE),
    sd_Fitbit.Heart_LE = sd(Fitbit.Heart_LE),
    mean_Fitbit_EE = mean(Fitbit.Calories_LE, na.rm = T),
    sd_Fitbit_EE = sd(Fitbit.Calories_LE),
    mean_Fitbit.Distance_LE = mean(Fitbit.Distance_LE),
    sd_Fitbit.Distance_LE = sd(Fitbit.Distance_LE),
    mean_EntropyFitbitHeartPerDay_LE = mean(EntropyFitbitHeartPerDay_LE),
    sd_EntropyFitbitHeartPerDay_LE = sd(EntropyFitbitHeartPerDay_LE),
    mean_EntropyFitbitStepsPerDay_LE = mean(EntropyFitbitStepsPerDay_LE),
    sd_EntropyFitbitStepsPerDay_LE = sd(EntropyFitbitStepsPerDay_LE),
    mean_RestingFitbitHeartrate_LE = mean(RestingFitbitHeartrate_LE),
    sd_RestingFitbitHeartrate_LE = sd(RestingFitbitHeartrate_LE),
    mean_CorrelationFitbitHeartrateSteps_LE = mean(CorrelationFitbitHeartrateSteps_LE, na.rm = T),
    sd_CorrelationFitbitHeartrateSteps_LE = sd(CorrelationFitbitHeartrateSteps_LE, na.rm = T),
    mean_NormalizedFitbitHeartrate_LE = mean(NormalizedFitbitHeartrate_LE),
    sd_NormalizedFitbitHeartrate_LE = sd(NormalizedFitbitHeartrate_LE),
    mean_FitbitIntensity_LE = mean(FitbitIntensity_LE),
    sd_FitbitIntensity_LE = sd(FitbitIntensity_LE),
    mean_SDNormalizedFitbitHR_LE = mean(SDNormalizedFitbitHR_LE),
    sd_SDNormalizedFitbitHR_LE = sd(SDNormalizedFitbitHR_LE),
    mean_FitbitStepsXDistance_LE = mean(FitbitStepsXDistance_LE),
    sd_FitbitStepsXDistance_LE = sd(FitbitStepsXDistance_LE)
  )

paper_stats <- round(paper_stats, 1)

write.csv(paper_stats, "descriptive_stats.csv")  
```

# Apple Watch Data

## Interpolated Results (Included in the paper)

### Decision Tree (Apple Watch)

```{r}
x_columns_AW_LE <- c(
  "age",
  "gender",
  "height",
  "weight",
  "Applewatch.Steps_LE",
  "Applewatch.Heart_LE",
  "Applewatch.Calories_LE",
  "Applewatch.Distance_LE",
  "EntropyApplewatchHeartPerDay_LE",
  "EntropyApplewatchStepsPerDay_LE",
  "RestingApplewatchHeartrate_LE",
  "CorrelationApplewatchHeartrateSteps_LE",
  "NormalizedApplewatchHeartrate_LE",
  "ApplewatchIntensity_LE",
  "SDNormalizedApplewatchHR_LE",
  "ApplewatchStepsXDistance_LE",
  "activity_trimmed"
)

x <- aggregated_data %>% select(x_columns_AW_LE)

write.csv(x, "aw_data_le_21_08_2019.csv", na = "")
x$gender <- ifelse(x$gender == "Male", 1, 0)

idx <- which(is.na(x), arr.ind = T)[, 1]
x <- x[-idx, ]

y <- as.factor(aggregated_data$activity_trimmed[-idx])

# y <- aggregated_data$activity_trimmed

train = sample(seq(length(y)), 0.7 * length(y))
test = seq(length(y))[-train]

train = x[train,]
train$activity_trimmed <- as.factor(train$activity_trimmed)

test = x[test,]
test$activity_trimmed <- as.factor(test$activity_trimmed)


dtModel <- rpart(activity_trimmed ~ ., train)

predict_unseen_aw_le <- predict(dtModel, test, type = 'class')

confusionMatrix(predict_unseen_aw_le, test$activity_trimmed)
```

### Random Forest

```{r}
x_columns_AW_LE <- c(
  "age",
  "gender",
  "height",
  "weight",
  "Applewatch.Steps_LE",
  "Applewatch.Heart_LE",
  "Applewatch.Calories_LE",
  "Applewatch.Distance_LE",
  "EntropyApplewatchHeartPerDay_LE",
  "EntropyApplewatchStepsPerDay_LE",
  "RestingApplewatchHeartrate_LE",
  "CorrelationApplewatchHeartrateSteps_LE",
  "NormalizedApplewatchHeartrate_LE",
  "ApplewatchIntensity_LE",
  "SDNormalizedApplewatchHR_LE",
  "ApplewatchStepsXDistance_LE"
 # ,"activity_trimmed"
)

x <- aggregated_data %>% select(x_columns_AW_LE)
x$gender <- ifelse(x$gender == "Male", 1, 0)

idx <- which(is.na(x), arr.ind = T)[, 1]
x <- x[-idx, ]

y <- as.factor(aggregated_data$activity_trimmed[-idx])

train = sample(seq(length(y)), 0.7 * length(y))
test = seq(length(y))[-train]

xTrain = x[train, ]
yTrain = y[train]
xTest = x[test, ]
yTest = y[test]

rfModel <- randomForest(x = xTrain, y = yTrain, ntree = 100)

### Training 
print(confusionMatrix(rfModel[["predicted"]], yTrain))

### Testing 
pred <- predict(rfModel, xTest)
print(confusionMatrix(pred, yTest))
```  
 
### SVM (Apple Watch)
```{r}
svmModel <- svm(xTrain, yTrain)

### Training
print(confusionMatrix(svmModel[["fitted"]], yTrain))

### Testing
pred <- predict(svmModel, xTest)
print(confusionMatrix(pred, yTest))
```

### Rotation Forest (Apple Watch)

Rotation Forest models were run in Weka and are available in the Github Repo. This code will only run if you have Weka [https://www.cs.waikato.ac.nz/ml/weka/](https://www.cs.waikato.ac.nz/ml/weka/) installed on your system.

```{r, eval=FALSE}
x_columns_AW_LE <- c(
  "age",
  "gender",
  "height",
  "weight",
  "Applewatch.Steps_LE",
  "Applewatch.Heart_LE",
  "Applewatch.Calories_LE",
  "Applewatch.Distance_LE",
  "EntropyApplewatchHeartPerDay_LE",
  "EntropyApplewatchStepsPerDay_LE",
  "RestingApplewatchHeartrate_LE",
  "CorrelationApplewatchHeartrateSteps_LE",
  "NormalizedApplewatchHeartrate_LE",
  "ApplewatchIntensity_LE",
  "SDNormalizedApplewatchHR_LE",
  "ApplewatchStepsXDistance_LE",
  "activity_trimmed"
)

x <- aggregated_data %>% select(x_columns_AW_LE)
x$gender <- ifelse(x$gender == "Male", 1, 0)

idx <- which(is.na(x), arr.ind = T)[, 1]
x <- x[-idx, ]


y <- aggregated_data$activity_trimmed

train = sample(seq(length(y)), 0.7 * length(y))
test = seq(length(y))[-train]

train = x[train,]
train$activity_trimmed <- as.factor(train$activity_trimmed)

test = x[test,]
test$activity_trimmed <- as.factor(test$activity_trimmed)


#load the RotationForest package as it's not from the default weka packages (note that the package should be installed before on weka using weka package manager)
WPM("load-package", "RotationForest")

# load the RotationForest classifier using RWeka
rotation_forest <- make_Weka_classifier("weka/classifiers/meta/RotationForest")

# generate the RotationForest model
rotationForestModel <- rotation_forest(activity_trimmed ~ ., train)

# predict the results
rotationForestPredict <- predict(rotationForestModel, test, type = 'class')

print(confusionMatrix(rotationForestPredict, test$activity_trimmed))
```


# FitBit Data

## Interpolated Results (Included in the paper)

### Decision Tree (Fitbit)
```{r}
x_columns_FB_LE <- c(
  "age",
  "gender",
  "height",
  "weight",
  "Fitbit.Steps_LE",
  "Fitbit.Heart_LE",
  "Fitbit.Calories_LE",
  "Fitbit.Distance_LE",
  "EntropyFitbitHeartPerDay_LE",
  "EntropyFitbitStepsPerDay_LE",
  "RestingFitbitHeartrate_LE",
  "CorrelationFitbitHeartrateSteps_LE",
  "NormalizedFitbitHeartrate_LE",
  "FitbitIntensity_LE",
  "SDNormalizedFitbitHR_LE",
  "FitbitStepsXDistance_LE",
  "activity_trimmed"
)

x <- aggregated_data %>% select(x_columns_FB_LE)
write_csv(x, "fb_data_le_21_08_2019.csv", na = "")
x$gender <- ifelse(x$gender == "Male", 1, 0)

y <- aggregated_data$activity_trimmed

train = sample(seq(length(y)), 0.7 * length(y))
test = seq(length(y))[-train]

train = x[train,]
train$activity_trimmed <- as.factor(train$activity_trimmed)

test = x[test,]
test$activity_trimmed <- as.factor(test$activity_trimmed)


dtModel <- rpart(activity_trimmed ~ ., train)
predict_unseen_fb_le <- predict(dtModel, test, type = 'class')

print(confusionMatrix(predict_unseen_fb_le, test$activity_trimmed))
```

### Random Forest (Fitbit)

```{r}
x_columns_FB_LE <- c(
  "age",
  "gender",
  "height",
  "weight",
  "Fitbit.Steps_LE",
  "Fitbit.Heart_LE",
  "Fitbit.Calories_LE",
  "Fitbit.Distance_LE",
  "EntropyFitbitHeartPerDay_LE",
  "EntropyFitbitStepsPerDay_LE",
  "RestingFitbitHeartrate_LE",
  "CorrelationFitbitHeartrateSteps_LE",
  "NormalizedFitbitHeartrate_LE",
  "FitbitIntensity_LE",
  "SDNormalizedFitbitHR_LE",
  "FitbitStepsXDistance_LE"
#  ,"activity_trimmed"
)

x <- aggregated_data %>% select(x_columns_FB_LE)
x$gender <- ifelse(x$gender == "Male", 1, 0)


idx <- which(is.na(x), arr.ind = T)[, 1]
x <- x[-idx, ]

# write.csv(x, "data_for_weka_fb.csv")


y <- as.factor(aggregated_data$activity_trimmed[-idx])

train = sample(seq(length(y)), 0.7 * length(y))
test = seq(length(y))[-train]

xTrain = x[train, ]
yTrain = y[train]
xTest = x[test, ]
yTest = y[test]

rfModel <- randomForest(x = xTrain, y = yTrain, ntree = 100)

### Training
print(confusionMatrix(rfModel[["predicted"]], yTrain))

### Testing
pred <- predict(rfModel, xTest)
print(confusionMatrix(pred, yTest))
```

  
### SVM (Fitbit)
```{r}
svmModel <- svm(xTrain, yTrain)
  
### Training
print(confusionMatrix(svmModel[["fitted"]], yTrain))

### Testing
pred <- predict(svmModel, xTest)
print(confusionMatrix(pred, yTest))
```

### Rotation Forest (Fitbit)

Rotation Forest models were run in Weka and are available in the Github Repo. This code will only run if you have Weka [https://www.cs.waikato.ac.nz/ml/weka/](https://www.cs.waikato.ac.nz/ml/weka/) installed on your system.

```{r, eval=FALSE}
x_columns_FB_LE <- c(
  "age",
  "gender",
  "height",
  "weight",
  "Fitbit.Steps_LE",
  "Fitbit.Heart_LE",
  "Fitbit.Calories_LE",
  "Fitbit.Distance_LE",
  "EntropyFitbitHeartPerDay_LE",
  "EntropyFitbitStepsPerDay_LE",
  "RestingFitbitHeartrate_LE",
  "CorrelationFitbitHeartrateSteps_LE",
  "NormalizedFitbitHeartrate_LE",
  "FitbitIntensity_LE",
  "SDNormalizedFitbitHR_LE",
  "FitbitStepsXDistance_LE",
  "activity_trimmed"
)

x <- aggregated_data %>% select(x_columns_FB_LE)
x$gender <- ifelse(x$gender == "Male", 1, 0)

idx <- which(is.na(x), arr.ind = T)[, 1]
x <- x[-idx, ]


y <- aggregated_data$activity_trimmed

train = sample(seq(length(y)), 0.7 * length(y))
test = seq(length(y))[-train]

train = x[train,]
train$activity_trimmed <- as.factor(train$activity_trimmed)

test = x[test,]
test$activity_trimmed <- as.factor(test$activity_trimmed)


#load the RotationForest package
WPM("load-package", "RotationForest")

# load the RotationForest classifier using RWeka
rotation_forest <- make_Weka_classifier("weka/classifiers/meta/RotationForest")

# generate the RotationForest model
rotationForestModel <- rotation_forest(activity_trimmed ~ ., train)

# predict the results
rotationForestPredict <- predict(rotationForestModel, test, type = 'class')

print(confusionMatrix(rotationForestPredict, test$activity_trimmed))
```


# Including device type as a feature

## Device name (Fitbit or Apple Watch) as a feature  

### Random Forest
```{r}
aggregated_data_appended <- read_csv("aggregated_fitbit_applewatch_jaeger_appended.csv")

x_columns_FB_LE <- c(
  "DeviceName",
  "age",
  "gender",
  "height",
  "weight",
  "Steps_LE",
  "Heart_LE",
  "Calories_LE",
  "Distance_LE",
  "EntropyHeartPerDay_LE",
  "EntropyStepsPerDay_LE",
  "RestingHeartrate_LE",
  "CorrelationHeartrateSteps_LE",
  "NormalizedHeartrate_LE",
  "Intensity_LE",
  "SDNormalizedHR_LE",
  "StepsXDistance_LE"
  #,"activity_trimmed"
)

x <- aggregated_data_appended %>% select(x_columns_FB_LE)
x$gender <- ifelse(x$gender == "Male", 1, 0)
x$DeviceName <- ifelse(x$DeviceName == "AppleWatch", 1, 0)


idx <- which(is.na(x), arr.ind = T)[, 1]
x <- x[-idx, ]

write.csv(x, "data_for_process.csv")


y <- as.factor(aggregated_data_appended$activity_trimmed[-idx])

train = sample(seq(length(y)), 0.7 * length(y))
test = seq(length(y))[-train]

xTrain = x[train, ]
yTrain = y[train]
xTest = x[test, ]
yTest = y[test]

rfModel <- randomForest(x = xTrain, y = yTrain, ntree = 100)

### Training
print(confusionMatrix(rfModel[["predicted"]], yTrain))

### Testing
pred <- predict(rfModel, xTest)
print(confusionMatrix(pred, yTest))
```

### SVM

```{r}
svmModel <- svm(xTrain, yTrain)

### Training
print(confusionMatrix(svmModel[["fitted"]], yTrain))

### Testing
pred <- predict(svmModel, xTest)
print(confusionMatrix(pred, yTest))
```


## Generating AppleWatch and Fitbit data for Rotation Forest model in Weka
```{r}
x_columns_AW_LE <- c(
  "age",
  "gender",
  "height",
  "weight",
  "Applewatch.Steps_LE",
  "Applewatch.Heart_LE",
  "Applewatch.Calories_LE",
  "Applewatch.Distance_LE",
  "EntropyApplewatchHeartPerDay_LE",
  "EntropyApplewatchStepsPerDay_LE",
  "RestingApplewatchHeartrate_LE",
  "CorrelationApplewatchHeartrateSteps_LE",
  "NormalizedApplewatchHeartrate_LE",
  "ApplewatchIntensity_LE",
  "SDNormalizedApplewatchHR_LE",
  "ApplewatchStepsXDistance_LE",
  "activity_trimmed"
)

x <- aggregated_data %>% select(x_columns_AW_LE)
x$gender <- ifelse(x$gender == "Male", 1, 0)

idx <- which(is.na(x), arr.ind = T)[, 1]
x <- x[-idx, ]

write.csv(x, "data_for_weka_aw.csv")

x_columns_FB_LE <- c(
  "age",
  "gender",
  "height",
  "weight",
  "Fitbit.Steps_LE",
  "Fitbit.Heart_LE",
  "Fitbit.Calories_LE",
  "Fitbit.Distance_LE",
  "EntropyFitbitHeartPerDay_LE",
  "EntropyFitbitStepsPerDay_LE",
  "RestingFitbitHeartrate_LE",
  "CorrelationFitbitHeartrateSteps_LE",
  "NormalizedFitbitHeartrate_LE",
  "FitbitIntensity_LE",
  "SDNormalizedFitbitHR_LE",
  "FitbitStepsXDistance_LE",
  "activity_trimmed"
)

x <- aggregated_data %>% select(x_columns_FB_LE)
x$gender <- ifelse(x$gender == "Male", 1, 0)


idx <- which(is.na(x), arr.ind = T)[, 1]
x <- x[-idx, ]

write.csv(x, "data_for_weka_fb.csv")
```


## Non-Interpolated Results (Not included in the paper)

### Applewatch with non-interpolated data - Decision tree
```{r}
x_columns_AW <- c(
  "age",
  "gender",
  "height",
  "weight",
  "Applewatch.Steps",
  "Applewatch.Heart",
  "Applewatch.Calories",
  "Applewatch.Distance",
  "EntropyApplewatchHeartPerDay",
  "EntropyApplewatchStepsPerDay",
  "RestingApplewatchHeartrate",
  "CorrelationApplewatchHeartrateSteps",
  "NormalizedApplewatchHeartrate",
  "ApplewatchIntensity",
  "SDNormalizedApplewatchHR",
  "ApplewatchStepsXDistance",
  "activity_trimmed"
)

x <- aggregated_data %>% select(x_columns_AW)
x$gender <- ifelse(x$gender == "Male", 1, 0)

y <- aggregated_data$activity_trimmed

train = sample(seq(length(y)), 0.7 * length(y))
test = seq(length(y))[-train]

train = x[train,]
train$activity_trimmed <- as.factor(train$activity_trimmed)

test = x[test,]
test$activity_trimmed <- as.factor(test$activity_trimmed)


dtModel <- rpart(activity_trimmed ~ ., train)
predict_unseen_aw <- predict(dtModel, test, type = 'class')

print(confusionMatrix(predict_unseen_aw, test$activity_trimmed))
```


##### Fitbit with non-interpolated data - Decision tree
```{r}
x_columns_FB <- c(
  "age",
  "gender",
  "height",
  "weight",
  "Fitbit.Steps",
  "Fitbit.Heart",
  "Fitbit.Calories",
  "Fitbit.Distance",
  "EntropyFitbitHeartPerDay",
  "EntropyFitbitStepsPerDay",
  "RestingFitbitHeartrate",
  "CorrelationFitbitHeartrateSteps",
  "NormalizedFitbitHeartrate",
  "FitbitIntensity",
  "SDNormalizedFitbitHR",
  "FitbitStepsXDistance",
  "activity_trimmed"
)

x <- aggregated_data %>% select(x_columns_FB)
x$gender <- ifelse(x$gender == "Male", 1, 0)

y <- aggregated_data$activity_trimmed

train = sample(seq(length(y)), 0.7 * length(y))
test = seq(length(y))[-train]

train = x[train,]
train$activity_trimmed <- as.factor(train$activity_trimmed)

test = x[test,]
test$activity_trimmed <- as.factor(test$activity_trimmed)


dtModel <- rpart(activity_trimmed ~ ., train)
predict_unseen_fb <- predict(dtModel, test, type = 'class')

print(confusionMatrix(predict_unseen_fb, test$activity_trimmed))
  
```


